\section*{Список литературы}
\addcontentsline{toc}{section}{Список литературы}
\begin{enumerate}[leftmargin=0em, itemindent=2.5 em,itemsep=1.5 pt,parsep=1.5 pt]

    \item R.Vargas, A. Mosavi, R. Ruiz. Deep Learning: A Review // Advances in \\ Intelligent Systems and Computing. -- 2017.
    \item D. Ross J.Lim R. Lin, Yang M. Incremental learning for robust visual tracking -- 2008.
    \item H. Grabner M. Grabner, Bischof H. Real-time tracking via on-line boosting // BMVC -- 2006. -- P.47-56.
    \item Y. Wu, J. Lim and M. Yang, Online Object Tracking: A Benchmark // IEEE Conference on Computer Vision and Pattern Recognition, Portland, OR, -- 2013. -- P. 2411-2418.
    \item H. Li C. Shen Q. Shi. Real-time visual tracking using compressive sensing. -- 2011. -- P.1305-1312.
    \item J. Kwon K. M. Lee. Minimum uncertainty gap for robust visual tracking. -- 2013. -- P.2355 -- 2362.
    \item Wang, Naiyan and Yeung, Dit-Yan. Learning a Deep Compact Image
    
    Representation for Visual Tracking // Curran Associates, Inc. -- 2013. -- 809 -- 817.
    \item Guoxing Wu. Regional deep learning model for visual tracking /  Wenjie Lu and Guangwei Gao and Chunxia Zhao and Jiayin Liu. // Neurocomputing -- 2016. -- P. 310 -- 323.
    \item A. Torralba, R. Fergus, and W. Freeman. 80 million tiny images: A large data set for nonparametric object and scene recognition. // IEEE Transactions on Pattern Analysis and Machine Intelligence, -- 2008. -- P.1958 -- 1970.
    \item Тарков М.С. Информационная ёмкость сети Хопфилда с квантованными весами // ПДМ -- 2019. -- Р. 97 -- 103.
\end{enumerate}